\section{Introduction}\label{intro}

It has long been known that star formation preferentially occurs within molecular clouds. 
Yet 
%mm the exact set-up that leads to the on-set of 
       the star formation process is still not completely understood.
It is clear that gravity is the major factor as it drives collapse motions and operates on all scales.
However, one needs additional processes that stabilise the gas
%mm
      or terminate star formation quickly 
in order to \textbf{explain low star formation efficiencies} observed in molecular clouds. 
Although there are many processes that act at the different scales of molecular clouds,
%mm turbulence is traditionally supposed 
     turbulent support has often been argued 
to be the best candidate for this task.

In the literature, turbulence has an ambiguous role in the context of star formation. 
In most of the cases, turbulence is expected to stabilise molecular clouds on large scales \citep{Fleck1980,McKee1992,MacLow2003}, while feedback processes and shear motions heavily destabilise or even disrupt cloud-like structures, offering a formation scenario for large filaments \citep{Tan2013,Miyamoto2014}. 
%mm ******[I don't really understand these cites to Tan & Miyamoto.  Usually I contrast large scale support with small-scale compressive promotion of collapse.]******
However, it remains unclear whether there are particular mechanisms that dominate the driving of turbulence within molecular clouds, \textbf{as every process is supposed to be traced by typical features in the observables.
Yet, these features are either not seen or are too ambiguous to clearly reflect the dominant driving mode.}
For example, turbulence that is driven by large-scale velocity dispersions during global collapse \citep{Ballesteros2011a,Ballesteros2011b,Hartmann2012} produces P-Cygni lines \textbf{ that have not yet been observed on scales of entire molecular clouds}. 
Internal feedback, on the contrary, seems more promising as it drives turbulence outwards \citep{Dekel2013,Krumholz2014}.
Observations, though, demonstrate that the required driving sources need to act on scales of entire clouds; which typical feedback\textbf{, such as radiation, winds, jets, or supernovae (SNe),} 
%mm processes 
cannot achieve \citep{Heyer2004,Brunt2009,Brunt2013}.

There have been many theoretical studies that have examined the nature and origin of turbulence within the phases of the interstellar medium \citep[ISM;][and references within]{MacLow2004}. 
The most established 
%mm work has been conducted
     characterization of turbulence in general was 
by \citet{Kolmogorov1941} who investigated fully developed, incompressible turbulence \textbf{driven on scales larger than the object of interest, and diffusing on scales much smaller than those of interest}.
In the scope of this paper this object is a single molecular cloud. 
%mm The underlying assumptions of \citeauthor{Kolmogorov1941}'s theory describe the very special scenario of a divergence-free velocity field. This is not necessarily the case in a molecular cloud, yet analytical studies without these assumptions are still rare, but exist. 
    Molecular clouds are highly compressible, though.  Only a few analytical studies have treated this case.
\citet{She1994} and \citet{Boldyrev2002}, for example, generalise and extend the predicted scaling of the decay of turbulence to supersonic turbulence.
\citet{Galtier2011} and \citet{Banerjee2013} provide an analytic description of the scaling of mass-weighted structure functions.

In this paper, we examine three molecular clouds that formed 
%mm self-similarly
   self-consistently from SN-driven turbulence 
in the simulations by \citet[\citetalias{IbanezMejia2016} and \citetalias{IbanezMejia2017} hereafter]{IbanezMejia2016,IbanezMejia2017} and study how the turbulence within the clouds' gas evolves.
The key questions we 
%mm answer 
    address
are the following: 
What dominates the turbulence within the simulated molecular clouds? 
\textbf{How can structure functions inform us about the evolutionary state of MCs and the dominant physics processes within them?}

In Sect.~\ref{methods}, we introduce the simulated clouds in the context of the underlying physics involved in the simulations.
Furthermore, we describe the theoretical basics of velocity structure functions.
Sect.~\ref{results} demonstrates that the velocity structure function is a useful tool to characterise the dominant driving mechanisms of turbulence in molecular clouds and can be applied to both simulated and observed data. 
We also discuss the influences of utilising one-dimensional velocity measurements, different Jeans refinement levels, density thresholds and density weighting on the applicability of the velocity structure function and the results obtained with it in Sect.~\ref{discussion}.  
We summarise our findings and conclusions in Sect.~\ref{conclusions}.



\endinput
